### 2015-09-10 fundamentals/examples.tex
converts to elsevier format
fixes misaligned quotes

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Cycic &  Input control - embedded in Cyclist & \cite{flanagan_input_2013}\\
Cyclist & Interactive data exploration environment & \cite{livnat_cyclist_2014} \\
Ciclus & Continuous integration scripts for \Cyclus & \cite{scopatz_ciclus_2014}\\
Cycstub & Skeleton for clean slate module development & \cite{carlsen_cycstub_2014}\\
Cyan & \Cyclus analysis tool & \cite{carlsen_cyan_2014}\\
Cloudlus & Tools for running \Cyclus in a cloud environment & \cite{carlsen_cloudlus_2014} \\
\hline
\end{tabularx}
\caption{Many tools have been developed outside of the scope of the \Cyclus kernel for improved user, developer, and analyst experiences with \Cyclus.}
\label{tab:coretools}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Bright-lite & A physics-based reactor archetype and fuel fabrication archetype & \cite{flanagan_bright-lite_2014} \\
Nuclear Fuel Inventory Model & A flexible, ORIGEN-based, reactor analysis module & \cite{skutnik_development_2015} \\
CommodConverter & A simple commodity converting storage facility archetype  & \cite{huff_commodconverter_2014} \\
MktDrivenInst & An institution that controls deployment based on commodity availability & \cite{huff_mktdriveninst_2014} \\
SeparationsMatrix & A facility for elemental separations of used fuel & \cite{huff_streamblender_2014} \\
StreamBlender & A facility for fuel fabrication from reprocessed streams & \cite{huff_streamblender_2014} \\
\hline
\end{tabularx}
\caption{A diverse set of archetypes under development reflect the diverse
needs of researchers at various institutions. These archetypes, contributed
outside of the \Cyclus core and \Cycamore libraries are the first demonstration
of community-driven development in a fuel cycle simulator.}
\label{tab:archetypes}
\end{table}

\subsection{Simulations}
\label{ref:simulations}
%Inpro example (is this still running or did we deprecate it with 1.0?)

@@

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|X|r|X|}
\hline
\textbf{Facility} &\textbf{Parameter} & \textbf{Value}\\
\hline
\textbf{LWR} & type & LWR\\
\Class{cycamore::Reactor} & batches & $3$ [batches/cycle]\\
                  & batch size & $20000$ [kg HM]\\
                  & cycle length & $18$ [months]\\
                  & refuelling time & $2$ [months]\\
                  & requests & recycled MOX (1st preference)\\
                  & requests & enriched UOX (2nd preference)\\
\hline
\textbf{Recycled Fuel Fabrication} & requests & depleted uranium\\
\Class{cycamore::Fab} & requests & separated fissile material\\
                      & offers & recycled MOX\\
\hline
\textbf{Separations} & requests & all spent fuel types \\
\Class{cycamore::Separations} & offers & separated fissile material\\
                      & efficiency & 0.99\\
                      & Pu separation capacity & $6.0E4$ [kg/month] \\
\hline
\textbf{Repository} & requests & all waste\\
\Class{cycamore::Sink} & capacity & $\infty$\\
\hline
\textbf{UOX Fabrication} & offers & UOX\\
\Class{cycamore::Source} & capacity & $\infty$\\
\hline
\textbf{DU Source} & offers & depleted U\\
\Class{cycamore::Source} & capacity & $\infty$\\
\hline
\end{tabularx}
\caption{Facility Configurations for Example Simulations}
\label{tab:facconfigs}
\end{table}

@@

    \item \textbf{Recycled Fuel Fabrication} (\Class{cycamore::Fab}): This
        facility requests depleted uranium and separated fissile material and
        mixes them together into recycled \gls{MOX} fuel that it offers to
        requesters.  The two streams are mixed in a ratio in order to match
        simple neutronics properties of the target fuel as closely as
        possible.  The method used is based on a variation "equivalence
        method" originally developed by Baker and Ross
        \cite{baker_comparison_1963}.  This technique has also been used in the
        \gls{COSI} fuel cycle simulator developed by the French \gls{CEA}.

@@

Cyclus' discrete materials make single-pass recycle straightforward to implement.  The
reactors keep track of fuel as discrete batches. A reactor remembers where it
received each batch from.  If a batch was received from the recycled fuel
fabrication facility, it does not offer it to separations and instead offers
it as a waste commodity which is only requested by the repository.  The
material flows for the Single-Pass Recycle case are shown in Figure
\ref{fig:flowmodopen}.

\begin{figure}[H]
\begin{center}
\includegraphics{./images/flow-mod-open-1.eps}
\end{center}
\caption{1-pass \gls{MOX} recycle scenario material flows.}
\label{fig:flowmodopen}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics{./images/flow-closed-1.eps}
\end{center}
\caption{Full \gls{MOX} recycle (multi-pass) fuel cycle material flows.}
\label{fig:flowclosed}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics{./images/puseries-1.eps}
\end{center}
\caption{System plutonium buildup with one reactor.}
\label{fig:puseries1}
\end{figure}

>>>>

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Cycic &  Input control - embedded in Cyclist & \cite{flanagan_input_2013}\\
Cyclist & Interactive data exploration environment & \cite{livnat_cyclist_2014} \\
Ciclus & Continuous integration scripts for \Cyclus & \cite{scopatz_ciclus_2014}\\
Cycstub & Skeleton for clean slate module development & \cite{carlsen_cycstub_2014}\\
Cyan & \Cyclus analysis tool & \cite{carlsen_cyan_2014}\\
Cloudlus & Tools for running \Cyclus in a cloud environment & \cite{carlsen_cloudlus_2014} \\
\hline
\end{tabularx}
\caption{Many tools have been developed outside of the scope of the \Cyclus kernel for improved user, developer, and analyst experiences with \Cyclus.}
\label{tab:coretools}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Bright-lite & A physics-based reactor archetype and fuel fabrication archetype & \cite{flanagan_bright-lite_2014} \\
Nuclear Fuel Inventory Model & A flexible, ORIGEN-based, reactor analysis module & \cite{skutnik_development_2015} \\
CommodConverter & A simple commodity converting storage facility archetype  & \cite{huff_commodconverter_2014} \\
MktDrivenInst & An institution that controls deployment based on commodity availability & \cite{huff_mktdriveninst_2014} \\
SeparationsMatrix & A facility for elemental separations of used fuel & \cite{huff_streamblender_2014} \\
StreamBlender & A facility for fuel fabrication from reprocessed streams & \cite{huff_streamblender_2014} \\
\hline
\end{tabularx}
\caption{A diverse set of archetypes under development reflect the diverse
needs of researchers at various institutions. These archetypes, contributed
outside of the \Cyclus core and \Cycamore libraries are the first demonstration
of community-driven development in a fuel cycle simulator.}
\label{tab:archetypes}
\end{table}

\subsection{Simulations}
\label{sec:simulations}
%Inpro example (is this still running or did we deprecate it with 1.0?)

@@

\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{|X|r|X|}
\hline
\textbf{Facility} &\textbf{Parameter} & \textbf{Value}\\
\hline
\textbf{LWR} & type & LWR\\
\Class{cycamore::Reactor} & batches & $3$ [batches/cycle]\\
                  & batch size & $20000$ [kg HM]\\
                  & cycle length & $18$ [months]\\
                  & refuelling time & $2$ [months]\\
                  & requests & recycled MOX (1st preference)\\
                  & requests & enriched UOX (2nd preference)\\
\hline
\textbf{Recycled Fuel Fabrication} & requests & depleted uranium\\
\Class{cycamore::Fab} & requests & separated fissile material\\
                      & offers & recycled MOX\\
\hline
\textbf{Separations} & requests & all spent fuel types \\
\Class{cycamore::Separations} & offers & separated fissile material\\
                      & efficiency & 0.99\\
                      & Pu separation capacity & $6.0E4$ [kg/month] \\
\hline
\textbf{Repository} & requests & all waste\\
\Class{cycamore::Sink} & capacity & $\infty$\\
\hline
\textbf{UOX Fabrication} & offers & UOX\\
\Class{cycamore::Source} & capacity & $\infty$\\
\hline
\textbf{DU Source} & offers & depleted U\\
\Class{cycamore::Source} & capacity & $\infty$\\
\hline
\end{tabularx}
\caption{Facility Configurations for Example Simulations}
\label{tab:facconfigs}
\end{table}

@@

    \item \textbf{Recycled Fuel Fabrication} (\Class{cycamore::Fab}): This
        facility requests depleted uranium and separated fissile material and
        mixes them together into recycled \gls{MOX} fuel that it offers to
        requesters.  The two streams are mixed in a ratio in order to match
        simple neutronics properties of the target fuel as closely as
        possible.  The method used is based on a variation ``equivalence
        method'' originally developed by Baker and Ross
        \cite{baker_comparison_1963}.  This technique has also been used in the
        \gls{COSI} fuel cycle simulator developed by the French \gls{CEA}.

@@

\Cyclus' discrete materials make single-pass recycle straightforward to implement.  The
reactors keep track of fuel as discrete batches. A reactor remembers where it
received each batch from.  If a batch was received from the recycled fuel
fabrication facility, it does not offer it to separations and instead offers
it as a waste commodity which is only requested by the repository.  The
material flows for the Single-Pass Recycle case are shown in Figure
\ref{fig:flowmodopen}.

\begin{figure}[H]
\begin{center}
\includegraphics[width=\textwidth]{./images/flow-mod-open-1.eps}
\end{center}
\caption{1-pass \gls{MOX} recycle scenario material flows.}
\label{fig:flowmodopen}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=\textwidth]{./images/flow-closed-1.eps}
\end{center}
\caption{Full \gls{MOX} recycle (multi-pass) fuel cycle material flows.}
\label{fig:flowclosed}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width=\textwidth]{./images/puseries-1.eps}
\end{center}
\caption{System plutonium buildup with one reactor.}
\label{fig:puseries1}
\end{figure}
